---
title: "R Notebook"
output: html_notebook
---

Code to illustrate fitting input distributions to data

```{r}
install.packages("fitdistrplus")
library(MASS)
library(fitdistrplus)
```

Use an in-built dataset
```{r}
data("groundbeef", package = "fitdistrplus")
my_data <- groundbeef$serving
plot(my_data, pch=20)
```

Plot histogram and density
```{r}
plotdist(my_data, histo = TRUE, demp = TRUE)
descdist(my_data, discrete=FALSE, boot=500) # describe the moments
```
Now, let's fit some distributions
```{r}
fit_w  <- fitdist(my_data, "weibull")
fit_g  <- fitdist(my_data, "gamma")
fit_ln <- fitdist(my_data, "lnorm")
summary(fit_ln)
print(fit_ln)
plot(fit_ln)
```
 
Plotting the results
```{r}
par(mfrow=c(2,2))
plot.legend <- c("Weibull", "lognormal", "gamma")
denscomp(list(fit_w, fit_g, fit_ln), legendtext = plot.legend)
cdfcomp (list(fit_w, fit_g, fit_ln), legendtext = plot.legend)
qqcomp  (list(fit_w, fit_g, fit_ln), legendtext = plot.legend)
ppcomp  (list(fit_w, fit_g, fit_ln), legendtext = plot.legend)
```

The fitting can work with other non-base distribution. In the next eg, the endosulfan dataset cannot be properly fit by the basic distributions like the log-normal:
```{r}
data("endosulfan", package = "fitdistrplus")
my_data <- endosulfan$ATV

fit_ln <- fitdist(my_data, "lnorm")
cdfcomp(fit_ln, xlogscale = TRUE, ylogscale = TRUE)
```
To solve this it is used the Burr and Pareto distributions available at package actuar
```{r}
install.packages("actuar")
library(actuar)

fit_ll <- fitdist(my_data, "llogis", start = list(shape = 1, scale = 500))
fit_P  <- fitdist(my_data, "pareto", start = list(shape = 1, scale = 500))
fit_B  <- fitdist(my_data, "burr",   start = list(shape1 = 0.3, shape2 = 1, rate = 1))
cdfcomp(list(fit_ln, fit_ll, fit_P, fit_B), xlogscale = TRUE, ylogscale = TRUE,
        legendtext = c("lognormal", "loglogistic", "Pareto", "Burr"), lwd=2)
```
Now, print some goodness of fit tests
```{r}
gofstat(list(fit_ln, fit_ll, fit_P, fit_B), fitnames = c("lnorm", "llogis", "Pareto", "Burr"))
```

Plotting distributions
name	description
dname( )	density or probability function
pname( )	cumulative density function
qname( )	quantile function
Rname( )	random deviates
```{r}
x <- seq(0, 1, length=100)
hx <- dbeta(x,1.5,5)
plot(x,hx,type="l")

```
